Hierarchical Controller Architecture for SDN

### 2013-11-05 presentation/ppt.tex
timestamp slide

\frame{
\frametitle{Timestamp}
	\begin{itemize}
		\item An example - Link Balancer Controller [4]
		\item On a flow arriving at an ingress port, a path with minimum maximum utilization is choosen
		\item Each domain i maintains a vector timestamp, conistsing of revision number of domains' link utilizations, seen so far
		\item When a flow path is set up at a domain, it is augmented by the timestamp of the domain
		\item Border routers in a domain may change a flow path if their timestamp is greater than flow's timestamp
		\item Flow's timestamp is updated as it passes through domains
		\item what if flow's timestamp is neither greater nor smaller than domain's timestamp ?
	\end{itemize}   
}

>>>>

\frame{
\frametitle{Timestamp}
	\begin{itemize}
		\item An example - Link Balancer Controller [4]
		\item On a flow arriving at an ingress port, a path with minimum maximum utilization is choosen
		\item Each domain $i$ maintains a vector timestamp, $T_{i}[1...n]$. $T_{i}[j]$ contains the latest revision number of domain $j$ link utilizations, seen by domain $i$
		\item Each router in a domain is updated with domain's timestamp
		\item When a flow path is being set up at domain $j$, it is augmented by the $T_{j}$
		\item When a router in a domain $i$ receives a flow with timestamp $T_{j}$, it may change part of flow's path if $T_{j}[i] < T_{i}[i]$ 
		\item Flow's timestamp is updated as $max\{T_{j}[k], T_{i}[k]\}$ , $k=1...n$ 
		\item OK, can we do better ? Yes!, a domain can change the entire flow's path according to timestamps.
	\end{itemize}   
}
